RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-09-14 validation.tex
forgot to push some changes

Table~\ref{table:survey:table2} shows the respondents' answers, the average score, the standard deviation, p-value, power, and effect size for questions Q5-Q7, and table~\ref{table:survey:table3} shows the results for questions Q8-Q10. We concluded with two open questions about the comparison between RationalGRL and other goal modeling languages. When asked about the advantages of RationalGRL over standard goal modeling languages, many users agreed that making arguments explicit may force end users to have a more structured discussion: ``	Clear communication about argumentation and forcing people to think in those clear terms.'', ``...you can add arguments and that you can answer questions that help you to develop arguments'', ``It's useful that discussion and explanation are close to the diagrams'', ``a way to see how decisions are being shaped.''. Furthermore, one user stated that RationalGRL successfully ``tries to capture the rationale behind the modeling process' and ``has a simple way to compute the status of the arguments''. When asked about the weaknesses, users mentioned the complexity as the most important weakness: ``The apparent increase in complexity might lead to negative perceptions'', ``adding yet another layer of complexity scares me''. One user mentioned that this may be a problem with goal modeling in general: ``Goal models are already complex (...) I have worked for years on the effect of context on goal models, and my conclusion is that this was very interesting academic work but with close-to-zero practical implications, unfortunately.''.

>>>>

Table~\ref{table:survey:table2} shows the respondents' answers, the average score, the standard deviation, p-value, power, and effect size for questions Q5-Q7, and Table~\ref{table:survey:table3} shows the results for questions Q8-Q10. We concluded with two open questions about the comparison between RationalGRL and other goal modeling languages. When asked about the advantages of RationalGRL over standard goal modeling languages, many users agreed that making arguments explicit may force end users to have a more structured discussion: ``	Clear communication about argumentation and forcing people to think in those clear terms.'', ``...you can add arguments and that you can answer questions that help you to develop arguments'', ``It's useful that discussion and explanation are close to the diagrams'', ``a way to see how decisions are being shaped.''. Furthermore, one user stated that RationalGRL successfully ``tries to capture the rationale behind the modeling process' and ``has a simple way to compute the status of the arguments''. When asked about the weaknesses, users mentioned the complexity as the most important weakness: ``The apparent increase in complexity might lead to negative perceptions'', ``adding yet another layer of complexity scares me''. One user mentioned that this may be a problem with goal modeling in general: ``Goal models are already complex (...) I have worked for years on the effect of context on goal models, and my conclusion is that this was very interesting academic work but with close-to-zero practical implications, unfortunately.''.
